---
title       : Predict Diamond Price 
subtitle    : Data Products Project 
author      : Anup Bera
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Factors for pricing a Diamond     
      
1. Diamond price is determined by several factors.
2. Collected Diamond dataset from the website http://www.pricescope.com/ 
3. From the Dataset, we choose 6 predictors : Shape, Carat, Cut, Color, Clarity & Depth
4. The Target variable is diamond **Price**
5. We will predict diamond price on the basis of the values of 6 predictors.

--- .class #id 

## Working in R
```{r}
data <- read.csv("Diamond_price.csv", header=TRUE)   
mydata <- data[, c(1,2,3,4,5,7,10)]     
str(mydata)      
```

--- .class #id 

## Analysis the Dataset

1. Random Forest model is used for diamond price prediction. Graph: Actual vs Predicted price.
```{r echo=FALSE,message=FALSE}
library(caret)
library(miscTools)
library(randomForest)
mydata$Price <- gsub('\\$', '', mydata$Price)
mydata$Price <- gsub(',', '', mydata$Price)
mydata$Price <- as.numeric(as.character(mydata$Price))
mydata <- mydata[mydata$Price <10000,]
model.forest <- train(Price~., mydata, method = "rf", trControl = trainControl(method = "cv", number = 3))
r2 <- rSquared(mydata$Price, mydata$Price - predict(model.forest, mydata))
ggplot(aes(x=actual, y=prediction),data=data.frame(actual=mydata$Price, prediction=predict(model.forest, mydata)))+ geom_point() +geom_abline(color="red") +ggtitle(paste("RandomForest Regression in R r^2=", round(r2,2), sep=""))
```

--- .class #id 

## Shiny APP
    
     
1. [Here](https://anupb08.shinyapps.io/DataProducts) you find the App.
2. Select the value of different predictors and press "Submit" button
3. You will get the result at the right side.




